\chapter{Acknowledgments}
I wish to express my gratitude to Prof.~Dr.~Andreas Wallraff and Dr.~Christopher Eichler for the opportunity of performing my master thesis at the Quantum Devices Lab, as well as for the continuous feedback on my work. These months have been a wonderful journey during which I acquired a significant amount of knowledge, and met many passionate, friendly and helpful people.

I particularly thank Dr.~Christian Andersen for his precious supervision and encouragements throughout my thesis. He introduced me to experiments with quantum computers, guided many of my steps, provided detailed feedback on my writings, and always found to time to answer my countless theoretical and conceptual questions. The achievements of this thesis would not have been possible without his guidance.

I extend my gratitude to Michele Collodo for his insightful remarks on many plots presented in this thesis, for his detailed feedback on the entire manuscript of this thesis, and for the myriad of quantum physics discussions. 

I appreciate the valuable contribution of Dr.~Christoph Hellings for the QAOA project since he joined in November 2019, which include but are not limited to improvements of the QAOA measurement code, insights in understanding QAOA landscape symmetries and tuning up the 7-qubit device in preparation of larger scale QAOA experiments.

I thank Ants Remm and Stefania Lazar for the considerable amount of their time they spent to introduce me to \texttt{pycQED}, the measurement framework used for these experiments. I also acknowledge the rest of the quantum computing team for their valuable input during Monday team meetings.

From the SuperQNet team, I particularily thank Paul Magnard and Kevin Reuer for relevant discussions on three-level, single-shot readout and active reset.

I extend my thanks to Carlotta Ruppert, Bruno Lacroix, Gauthier Muguerza and Vadim Lacroix for their proofreading and feedback of the manuscript of this thesis.

Finally, I extremely grateful to Carlotta Ruppert and my family for their continuous support throughout this thesis.